\documentclass[11pt,a4paper]{extarticle}
\usepackage[top=0.9cm,bottom=0.9cm,left=1.2cm,right=1.2cm]{geometry}
\usepackage{xcolor}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=blue]{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{enumitem}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\definecolor{cvgray}{RGB}{55,55,55}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagenumbering{gobble}
\newcommand{\cvsection}[1]{%
  \vspace{0.10cm}
  \begin{center}
    \rule{3.5cm}{0.5pt}\hspace{0.30cm}{\large\bfseries #1}\hspace{0.30cm}\rule{3.5cm}{0.5pt}
  \end{center}
  \vspace{0.05cm}
}
\newcommand{\entry}[4]{%
\noindent\begin{tabularx}{\textwidth}{@{}p{0.25\textwidth}X@{}}
\textbullet\ \textbf{#1} & \textbf{#3} \\
\hspace*{0.45cm}\small #2 & \small #4 \\
\end{tabularx}\par\vspace{0.10cm}\par\noindent\ignorespaces
}
\newcommand{\skillgroup}[2]{%
\textbf{#1}\par\vspace{0.02cm}%
\begin{list}{\textbullet}{\leftmargin=0.55cm \itemindent=0pt \labelsep=0.15cm \itemsep=0pt \parsep=0pt \topsep=0pt}%
\small #2\normalsize
\end{list}%
\vspace{0.05cm}\noindent\ignorespaces
}
\begin{document}
\begin{center}
{\Large\bfseries\color{cvgray} CHEIKH SEYIDI MOHAMED JEDOU}\\[0.15cm]
{\normalsize AI Engineer \,\textbar\, Machine Learning \,\textbar\, Computer Vision \,\textbar\, Multi-Agent Systems}
\end{center}
\vspace{-0.10cm}
\begin{center}
{\large\bfseries Personal Details:}\\[0.12cm]
\textbf{Phone:} +222 37 88 08 85 \quad | \quad
\textbf{Email:} \href{mailto:chkseyidi@gmail.com}{chkseyidi@gmail.com} \quad | \quad
\textbf{Address:} Nouakchott, Mauritania
\end{center}
\cvsection{Education}
\entry{2022 -- 2024}{Dakar, Senegal}
{Master's Degree in Artificial Intelligence and Big Data}
{Cheikh Anta Diop University, ESP.}
\entry{2019 -- 2022}{Nouakchott, Mauritania}
{Bachelor's Degree in Mathematics and Computer Science}
{University of Nouakchott Al Asriya, FST.}
\cvsection{Professional Experience}
\entry{2025 -- 2026}{Nouakchott}
{AI Engineer -- \href{https://www.smartmssa.com/}{Smart MS SA}:}
{Architected and shipped production AI systems spanning Machine Learning, Computer Vision, and NLP for low-resource environments --- combining custom embeddings, vision pipelines, and multi-agent orchestration. Owned the full model lifecycle from training through deployment in environments where pre-trained models don't exist.}
\entry{2024}{Nouakchott}
{AI Intern -- GARini Project, \href{https://mtnima.gov.mr}{Ministry of Digital Transformation}:}
{Developed GARini, an intelligent educational assistant built with Django. Designed semantic search pipelines with FAISS vector indexing, custom embeddings, and contextual reasoning to deliver accurate, domain-specific educational responses. Implemented response evaluation and quality control mechanisms for agentic workflows.}
\entry{2022}{Nouakchott}
{Research Data Engineering -- PEV Sahel Project, G5 Sahel:}
{Research data engineering for a G5 Sahel / Coventry University field investigation, in collaboration with the University of Nouakchott Al Asriya. Built pipelines for collection, cleaning, validation, and analytical visualization --- supporting investigator training and ensuring data integrity across the study.}
\entry{Current}{Remote}
{Freelance -- Autonomous AI Agents \& Multi-Agent Systems:}
{Designing autonomous agents and multi-agent systems: custom orchestration logic, multi-step planning, tool use and function calling, persistent memory, and execution loops with error recovery and self-correction. Selective freelance engagements on hard agent problems.}
\cvsection{Technical Skills}
\noindent\begin{tabularx}{\textwidth}{@{}XXX@{}}
\skillgroup{Machine Learning}{%
\item PyTorch
\item Scikit-learn
\item XGBoost \& LightGBM
\item Feature engineering
\item Transformer architectures
\item Transfer learning}
&
\skillgroup{Computer Vision}{%
\item OpenCV
\item YOLO / Ultralytics
\item Image segmentation
\item Vision Transformers (ViT)
\item Data augmentation
\item Transfer learning (vision)}
&
\skillgroup{NLP \& LLMs}{%
\item PEFT / LoRA fine-tuning
\item Custom embeddings
\item Tokenizer design
\item Low-resource NLP
\item Model evaluation
\item Quantization \& distillation}
\\
\skillgroup{Agents \& Orchestration}{%
\item Multi-agent systems
\item Tool use \& function calling
\item Multi-step planning
\item Custom orchestration
\item Persistent memory
\item Self-correction loops}
&
\skillgroup{Semantic Search \& Retrieval}{%
\item FAISS · Qdrant
\item Vector indexing
\item Semantic search
\item Contextual reasoning
\item Hybrid retrieval
\item Domain-specific pipelines}
&
\skillgroup{Engineering \& MLOps}{%
\item Python
\item FastAPI · Django
\item Docker
\item Hugging Face ecosystem
\item ML pipelines
\item Production deployment}
\\
\end{tabularx}
\cvsection{Languages}
\begin{center}
\begin{tabularx}{0.90\textwidth}{XXX}
\textbullet\ \textbf{English} & \textbullet\ \textbf{Français} & \textbullet\ \textbf{Arabic} \\
Advanced & Advanced & Advanced \\
\end{tabularx}
\end{center}
\end{document}
